A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-24 03-semantics.tex
Conserta a legenda da Figura 4 na Seção 3

\begin{figure}[h]
\small
\begin{gather*}
  \boxed{
    \begin{align*}
      %%
      %%-
      \intertext{\llap{(i)~}Function~$\bcast$:}
      %%-
      %%
      \bcast(\ceu{\AwaitExt(e)},e)
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \bcast(\ceu{\AwaitInt(e)},e)
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \bcast(\ceu{\Every{e}\ {p}},e)
      &=\ceu{p;\,\Every{e}\ {p}}\\[-1\jot]
      %%
      \bcast(\ceu{\CanRun(n)},e)
      &=\ceu{\CanRun(n)}\\[-1\jot]
      %%
      \bcast(\ceu{\Fin{p}},e)
      &=\ceu{\Fin{p}}\\[-1\jot]
      %%
      \bcast(\ceu{p;\,q})
      &=\ceu{\bcast(p,e);\,q}\\[-1\jot]
      %%
      \bcast(\ceu{p\AtLoop{q}},e)
      &=\ceu{\bcast(p,e)\AtLoop{q}}\\[-1\jot]
      %%
      \bcast(\ceu{p\AtAnd{q}},e)
      &=\ceu{{\bcast(p,e)}\AtAnd{\bcast(q,e)}}\\[-1\jot]
      %%
      \bcast(\ceu{p\AtOr{q}},e)
      &=\ceu{{\bcast(p,e)}\AtOr{\bcast(q,e)}}\\[-1\jot]
      %%
      bcast(\_,e)
      &=\_\enspace
        (\ceu{\Mem},\ceu{\EmitInt},\ceu{\Break},\\[-1\jot]
      &\quad\ceu{\IfElse{}{}},\ceu{\Loop},\ceu{\And},\ceu{\Or},\ceu{\Nop})
      \\[1\jot]
      %%
      %%-
      \intertext{\llap{(ii)~}Predicate~$\isblocked$:}
      %%-
      %%
      \isblocked(\ceu{\AwaitExt(e)},n)
      &=\mathit{true}\\[-1\jot]
      %%
      \isblocked(\ceu{\AwaitInt(e)},n)
      &=\mathit{true}\\[-1\jot]
      %%
      \isblocked(\ceu{\Every{e}\ {p}},n)
      &=\mathit{true}\\[-1\jot]
      %%
      \isblocked(\ceu{\CanRun(m)},n)
      &=(n>m)\\[-1\jot]
      %%
      \isblocked(\ceu{\Fin{p}},n)
      &=\mathit{true}\\[-1\jot]
      %%
      \isblocked(\ceu{p;\,q},n)
      &=\isblocked(p,n)\\[-1\jot]
      %%
      \isblocked(\ceu{p\AtLoop{q}},n)
      &=\isblocked(p,n)\\[-1\jot]
      %%
      \isblocked(\ceu{p\AtAnd{q}},n)
      &=\isblocked(p,n)\land\isblocked(q,n)\\[-1\jot]
      %%
      \isblocked(\ceu{p\AtOr{q}},n)
      &=\isblocked(p,n)\land\isblocked(q,n)\\[-1\jot]
      %%
      \isblocked(\_,n)
      &=\mathit{false}\enspace
        (\ceu{\Mem},\ceu{\EmitInt},\ceu{\Break},\\[-1\jot]
      &\quad\ceu{\IfElse{}{}},\ceu{\Loop},\ceu{\And},\ceu{\Or},\ceu{\Nop})
        \\[1\jot]
      %%
      %%-
      \intertext{\llap{(iii)~}Function~$\clear$:}
      %%-
      %%
      \clear(\ceu{\AwaitExt(e)})
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \clear(\ceu{\AwaitInt(e)})
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \clear(\ceu{\Every{e}\ p})
      %%
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \clear(\ceu{\CanRun(n)})
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \clear(\ceu{\Fin{p}})
      &=p\\[-1\jot]
      %%
      \clear(\ceu{p;\,q})
      &=\clear(p)\\[-1\jot]
      %%
      \clear(\ceu{p\AtLoop{q}})
      &=\clear(p)\\[-1\jot]
      %%
      \clear(\ceu{p\AtAnd{q}})
      &=\ceu{\clear(p);\,\clear(q)}\\[-1\jot]
      %%
      \clear(\ceu{p\AtOr{q}})
      &=\ceu{\clear(p);\,\clear(q)}\\[-1\jot]
      %%
      \clear(\_)
      &=\bot\enspace
        (\ceu{\Mem},\ceu{\EmitInt},\ceu{\Break},\\[-1\jot]
      &\quad\ceu{\IfElse{}{}},\ceu{\Loop},\ceu{\And},\ceu{\Or},\ceu{\Nop})
    \end{align*}}
\end{gather*}
\vskip-2\belowdisplayskip
\caption{%
  (i)~Function~$\bcast$ awakes awaiting trails matching the event by
  converting~$\ceu{\protect\AwaitExt}$ and~$\ceu{\protect\AwaitInt}$
  to~$\ceu{\protect\Nop}$ expressions, and by unwinding $\ceu{\protect\Every}$
  expressions.
  %%
  \enspace(ii)~Predicate~$\isblocked$ is true only if all branches in parallel
  are blocked waiting for events, for finalization clauses, or for certain
  stack levels.
  %%
  \enspace(iii)~Function~$\clear$ extracts~$\ceu{\protect\Fin}$ expressions in
  parallel and put their bodies in sequence.
}
\label{fig.bcast}
\label{fig.isblocked}
\label{fig.clear}
\end{figure}

>>>>

\begin{figure}[h]
\small
\begin{gather*}
  \boxed{
    \begin{align*}
      %%
      %%-
      \intertext{\llap{(i)~}Function~$\bcast$:}
      %%-
      %%
      \bcast(\ceu{\AwaitExt(e)},e)
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \bcast(\ceu{\AwaitInt(e)},e)
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \bcast(\ceu{\Every{e}\ {p}},e)
      &=\ceu{p;\,\Every{e}\ {p}}\\[-1\jot]
      %%
      \bcast(\ceu{\CanRun(n)},e)
      &=\ceu{\CanRun(n)}\\[-1\jot]
      %%
      \bcast(\ceu{\Fin{p}},e)
      &=\ceu{\Fin{p}}\\[-1\jot]
      %%
      \bcast(\ceu{p;\,q})
      &=\ceu{\bcast(p,e);\,q}\\[-1\jot]
      %%
      \bcast(\ceu{p\AtLoop{q}},e)
      &=\ceu{\bcast(p,e)\AtLoop{q}}\\[-1\jot]
      %%
      \bcast(\ceu{p\AtAnd{q}},e)
      &=\ceu{{\bcast(p,e)}\AtAnd{\bcast(q,e)}}\\[-1\jot]
      %%
      \bcast(\ceu{p\AtOr{q}},e)
      &=\ceu{{\bcast(p,e)}\AtOr{\bcast(q,e)}}\\[-1\jot]
      %%
      bcast(\_,e)
      &=\_\enspace
        (\ceu{\Mem},\ceu{\EmitInt},\ceu{\Break},\\[-1\jot]
      &\quad\ceu{\IfElse{}{}},\ceu{\Loop},\ceu{\And},\ceu{\Or},\ceu{\Nop})
      \\[1\jot]
      %%
      %%-
      \intertext{\llap{(ii)~}Predicate~$\isblocked$:}
      %%-
      %%
      \isblocked(\ceu{\AwaitExt(e)},n)
      &=\mathit{true}\\[-1\jot]
      %%
      \isblocked(\ceu{\AwaitInt(e)},n)
      &=\mathit{true}\\[-1\jot]
      %%
      \isblocked(\ceu{\Every{e}\ {p}},n)
      &=\mathit{true}\\[-1\jot]
      %%
      \isblocked(\ceu{\CanRun(m)},n)
      &=(n>m)\\[-1\jot]
      %%
      \isblocked(\ceu{\Fin{p}},n)
      &=\mathit{true}\\[-1\jot]
      %%
      \isblocked(\ceu{p;\,q},n)
      &=\isblocked(p,n)\\[-1\jot]
      %%
      \isblocked(\ceu{p\AtLoop{q}},n)
      &=\isblocked(p,n)\\[-1\jot]
      %%
      \isblocked(\ceu{p\AtAnd{q}},n)
      &=\isblocked(p,n)\land\isblocked(q,n)\\[-1\jot]
      %%
      \isblocked(\ceu{p\AtOr{q}},n)
      &=\isblocked(p,n)\land\isblocked(q,n)\\[-1\jot]
      %%
      \isblocked(\_,n)
      &=\mathit{false}\enspace
        (\ceu{\Mem},\ceu{\EmitInt},\ceu{\Break},\\[-1\jot]
      &\quad\ceu{\IfElse{}{}},\ceu{\Loop},\ceu{\And},\ceu{\Or},\ceu{\Nop})
        \\[1\jot]
      %%
      %%-
      \intertext{\llap{(iii)~}Function~$\clear$:}
      %%-
      %%
      \clear(\ceu{\AwaitExt(e)})
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \clear(\ceu{\AwaitInt(e)})
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \clear(\ceu{\Every{e}\ p})
      %%
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \clear(\ceu{\CanRun(n)})
      &=\ceu{\Nop}\\[-1\jot]
      %%
      \clear(\ceu{\Fin{p}})
      &=p\\[-1\jot]
      %%
      \clear(\ceu{p;\,q})
      &=\clear(p)\\[-1\jot]
      %%
      \clear(\ceu{p\AtLoop{q}})
      &=\clear(p)\\[-1\jot]
      %%
      \clear(\ceu{p\AtAnd{q}})
      &=\ceu{\clear(p);\,\clear(q)}\\[-1\jot]
      %%
      \clear(\ceu{p\AtOr{q}})
      &=\ceu{\clear(p);\,\clear(q)}\\[-1\jot]
      %%
      \clear(\_)
      &=\xi\enspace
        (\ceu{\Mem},\ceu{\EmitInt},\ceu{\Break},\\[-1\jot]
      &\quad\ceu{\IfElse{}{}},\ceu{\Loop},\ceu{\And},\ceu{\Or},\ceu{\Nop})
    \end{align*}}
\end{gather*}
\vskip-2\belowdisplayskip
\caption{%
  (i)~Function~$\bcast$ awakes awaiting trails matching the event by
  converting~$\ceu{\protect\AwaitExt}$ and~$\ceu{\protect\AwaitInt}$
  to~$\ceu{\protect\Nop}$, and by unwinding $\ceu{\protect\Every}$
  expressions.
  %%
  \space(ii)~Predicate~$\isblocked$ is true only if all branches in parallel
  are blocked waiting for events, finalization clauses, or certain
  stack levels.
  %%
  \space(iii)~Function~$\clear$ extracts~$\ceu{\protect\Fin}$ expressions in
  parallel and put their bodies in sequence.
  %%
  In~(i), (ii), and~(iii),~``$\_$'' denotes the omitted cases and~``$\xi$''
  denotes the empty string.
  %%
}
\label{fig.bcast}
\label{fig.isblocked}
\label{fig.clear}
\end{figure}
